---
title: "p8105_hw5_zw2709"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data.

```{r, message= FALSE}
homicide_df = 
  read_csv("homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```






## Problem 2 


import one dataset 

```{r}
data_1 = read_csv("data/con_01.csv")
```


create the dataframe 

```{r, error = TRUE, message= FALSE}
path_df = 
  tibble(
    path = list.files("data"),
  ) %>%    # dataframe containing all file names
  mutate(
    path = str_c("data/", path),
    data = map(path, read_csv)) %>%  # Iterate over file names and read in data for each subject, saved in the new variable "data"
  unnest(data)

```

The dataframe containing data from all participants is as follows:
```{r, message = FALSE}
path_df
```

Tidy the dataframe
```{r}
df = 
  path_df %>% 
  mutate(
    path = str_replace(path, "data/", ""),
    path = str_replace(path, ".csv", "")
  ) %>% 
  separate(path, into = c("arm", "subjectID"), sep = "_") %>% 
  mutate(
    arm = str_replace(arm, "con", "control"),
    arm = str_replace(arm, "exp", "experiment"),
    subjectID = as.numeric(subjectID)
  ) %>% 
  
  pivot_longer(
    week_1:week_8,
    names_to = "weeks",
    values_to = "observations"
  ) %>% 
  
  mutate(
    weeks = str_replace(weeks, "week_", ""),
    weeks = as.numeric(weeks)
  )

df
```


Make a spaghetti plot showing observations on each subject over time

```{r}
df %>% 
  
  ggplot(aes(x = weeks, y = observations, color = subjectID)) +
  geom_point(alpha = 0.5, size = 0.1)+
  geom_path()+
  facet_grid(. ~ arm)+
  
  labs(
    title = "plot showing observations on each subject over time",
    x = "weeks",
    y = "observations"
  ) +
  theme_minimal()
  
```

Over the 8 weeks of observation period, the experiment group seems to have an increasing tread with some fluctuations. The control group have changing values during the period, but the values from the beginning and the end do not have a large difference.



## Problem 3

write a function 
```{r}
simulation = function(n = 30, mu, sigma = 5){
  
 data = 
    tibble(
      x = rnorm(n = 30, mean = mu, sd = sigma)
    )
  
 test = 
   t.test(data, conf.level = 0.95) %>% 
   broom::tidy() 
  
  data %>% 
    summarise(
     mu_hat = mean(x), 
     p_value = test$p.value
    )
  
}
```


do the iteration--generate 5000 dataset (mu = 0)
```{r}
results_mu_0 = 
  rerun(5000, simulation(mu = 0)) %>% 
  bind_rows()

results_mu_0
```



Repeat the above for μ={1,2,3,4,5,6}

```{r}
simulation_result = 
  tibble(
    mu = c(1,2,3,4,5,6)
  ) %>% 
  
  mutate(
    output_lists = map(.x = mu, ~ rerun(5000, simulation(mu = .x))),
    estimate_df = map(output_lists, bind_rows)
  ) %>% 
  
  select(-output_lists) %>% 
  unnest(estimate_df)
```


* first plot
Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r, message= FALSE}
reject = 
  simulation_result %>% 
  filter(p_value < 0.05) %>% 
  
  group_by(mu) %>% 
  summarize(
    reject = n()
  ) %>% 
  mutate(
    reject_prop = reject / 5000
  )

reject
```

```{r}
reject %>% 
  
  ggplot(aes(x = mu, y = reject_prop)) +
  geom_point(alpha = 0.5, size = 0.1)+
  geom_path()+
  
  labs(
    title = "plot showing the proportion of rejection and true mu value",
    x = "mu values",
    y = "proportion of rejection"
  ) +
  theme_minimal()
  
```

With the increase of the true value of mu, the proportion of rejection(times of rejecting the null hypothesis) increases. When mu is equal to 6, it's certain to have rejection(proportion equals to 1). The power(probability of rejecting false null hypothesis) seems to be positively associated with the effect size.





* second plot
```{r}
average_mu = 
  simulation_result %>% 
  
  group_by(mu) %>% 
  summarise(
    average_mu = mean(mu_hat)
  )


average_mu_reject = 
  simulation_result %>% 
  filter(p_value < 0.05) %>%
  
  group_by(mu) %>% 
  summarise(
    average_mu_reject = mean(mu_hat)
  )
  
```


```{r}
average_mu %>% 
  ggplot(aes(x = mu, y = average_mu)) +
  geom_point(alpha = 0.5, size = 0.1)+
  geom_path()+
  
  labs(
    title = "average u_hat and true mu value",
    x = "mu values",
    y = "average estimate of u_hat"
  ) +
  theme_minimal()
```

```{r}
average_mu_reject %>% 
  ggplot(aes(x = mu, y = average_mu_reject)) +
  geom_point(alpha = 0.5, size = 0.1)+
  geom_path()+
  
  labs(
    title = "average u_hat in samples rejecting the null and true mu value",
    x = "mu values",
    y = "average estimate of u_hat in samples rejecting the null"
  ) +
  theme_minimal()
```

